---
title: "graphic_description"
categories:
  - Data Sciences I
description: |
  A short description of the post.
author:
  - name: Bayaert Wendy-Shirley
    url: {}
date: 11-10-2020
output:
  distill::distill_article:
    self_contained: false
---

```{r setup, include=FALSE}
SciViews::R
knitr::opts_chunk$set(echo = FALSE)
```

```{r importation}
data <- read("zooplankton", package = "data.io")
```

Distill is a publication format for scientific and technical writing, native to the web.

Learn more about using Distill at <https://rstudio.github.io/distill>.

# Introduction

The study was realised thanks to a data frame with 19 variables on samples of zooplankton originating from Tulear in Madagascar, including the taxonomic classification.
Those various features was measured by image analysis with the package zooimage and ImageJ. 
Those organisms originate from various samples (different seasons, depth, etc.) to take the variability into account. -> *A arranger (grammaire) !*

# Analysis

Graphique en anglais + commentaire (2-3 lignes)

